Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-18 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
引用算法
将 the location of 改为 the location and size of

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{images/network_v4.png}
\caption{The pipeline of the proposed method. We aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the fake target $p$ to $\textbf x$, the tracker outputs the location of the adversarial patch instead of the real target.}
\label{fig:net}
\end{figure}

@@

\textcolor{black}{In this section, we introduce our universal targeted attack framework for object trackers based on Siamese networks. We aim to attack the tracker by adding an imperceptible perturbation to the template image and pasting a \textit{fake target}, i.e., an adversarial patch into the search image adhering to the predefined trajectory, so that the tracker outputs the location of the fake target instead of the real target. Below, we formalize the task of performing universal targeted attacks on an object tracker, and then introduce our perturbation strategy in detail.}

@@

Formally, we aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the fake target $p$ to $\textbf x$, the tracker outputs the location of the adversarial patch instead of the real target (see Figure \ref{fig:net}).
Both $\delta$ and $p$ are universal (i.e., video-agnostic), which means perturbing a new video only involves the mere addition/paste of the perturbations to the template/search image -- and does not require gradient optimisation or network inference.

@@

In this subsection, we show how to train the universal perturbations $(\delta, p)$ for Siamese trackers.
During the $k$-th iteration of training, a video $V=\{I_i\}_1^T$ is randomly selected from the training dataset $\mathcal V$. Assuming the template perturbation at the $k$-th iteration is $\delta_k \in \mathbb{R}^{127\times 127 \times 3}$, and the adversarial patch is $p_k \in \mathbb{R}^{128\times 128\times 3}$. We first randomly pick two frames $I_t, I_s$ from $V$.
The clean template image $\textbf z\in \mathbb{R}^{127\times 127 \times 3}$ is generated according to $I_t$ and $b^{gt}_t$, and the perturbed template image is:
\begin{equation}
\tilde {\textbf z} = \textbf z + \delta_i.
\end{equation}
Similarly, the clean search image $\textbf x \in \mathbb{R}^{303\times 303 \times 3}$ is generated according to $I_s$ and $b^{gt}_s$.
As mentioned before, the patch is regarded as a fake target and pasted on the search image. We force the center position of the fake target to near the center position of the real target (i.e., the center of the search image) with a shift of 64 pixels, where shift is defined as the max range of translation generated by a uniform distribution.
%an offset $(\Delta_x, \Delta_y)$.
%We set this offset to $(\pm 64, \pm 64)$. 
%$\Delta_x$ (as well as $\Delta_y$) is randomly selected between -64 pixels and 64 pixels.
The width/height of the fake target is randomly selected between 32 pixels and 128 pixels.
The perturbed search image is generated as follows:
\begin{equation}
\tilde{\textbf x} = A(\textbf x, p_k, (l^x, l^y), (w, h)),
\end{equation}
where $(l^x, l^y)$ and $(w, h)$ represents the position and size of the fake target relative to the search image, respectively. $A$ is patch application operator \cite{patch} which first resizes the patch $p_k \in \mathbb{R}^{128\times 128\times 3}$ to $\hat{p}_k \in \mathbb{R}^{w\times h\times 3}$, and then applies the resized patch $\hat{p}_k$ to the search image $\textbf x$ at location $(l^x,l^y)$.

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.48\textwidth]{images/network_v4.png}
\caption{The pipeline of the proposed method. We aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the fake target $p$ to $\textbf x$, the tracker outputs the location and size of the adversarial patch instead of the real target.}
\label{fig:net}
\end{figure}

@@

\textcolor{black}{In this section, we introduce our universal targeted attack framework for object trackers based on Siamese networks. We aim to attack the tracker by adding an imperceptible perturbation to the template image and pasting a \textit{fake target}, i.e., an adversarial patch into the search image adhering to the predefined trajectory, so that the tracker outputs the location and size of the fake target instead of the real target. Below, we formalize the task of performing universal targeted attacks on an object tracker, and then introduce our perturbation strategy in detail.}

@@

Formally, we aim to train an imperceptible perturbation $\delta$ for the template image $\textbf z$, and an adversarial patch $p$ for the search image $\textbf x$. After adding $\delta$ to $\textbf z$ and pasting the fake target $p$ to $\textbf x$, the tracker outputs the location and size of the adversarial patch instead of the real target (see Figure \ref{fig:net}).
Both $\delta$ and $p$ are universal (i.e., video-agnostic), which means perturbing a new video only involves the mere addition/paste of the perturbations to the template/search image -- and does not require gradient optimisation or network inference.

@@

In this subsection, we show how to train the universal perturbations $(\delta, p)$ for Siamese trackers (see Algorithm 1).
During the $k$-th iteration of training, a video $V=\{I_i\}_1^T$ is randomly selected from the training dataset $\mathcal V$. Assuming the template perturbation at the $k$-th iteration is $\delta_k \in \mathbb{R}^{127\times 127 \times 3}$, and the adversarial patch is $p_k \in \mathbb{R}^{128\times 128\times 3}$. We first randomly pick two frames $I_t, I_s$ from $V$.
The clean template image $\textbf z\in \mathbb{R}^{127\times 127 \times 3}$ is generated according to $I_t$ and $b^{gt}_t$, and the perturbed template image is:
\begin{equation}
\tilde {\textbf z} = \textbf z + \delta_i.
\end{equation}
Similarly, the clean search image $\textbf x \in \mathbb{R}^{303\times 303 \times 3}$ is generated according to $I_s$ and $b^{gt}_s$.
As mentioned before, the patch is regarded as a fake target and pasted on the search image. We force the center position of the fake target to near the center position of the real target (i.e., the center of the search image) with a shift of 64 pixels, where shift is defined as the max range of translation generated by a uniform distribution.
%an offset $(\Delta_x, \Delta_y)$.
%We set this offset to $(\pm 64, \pm 64)$. 
%$\Delta_x$ (as well as $\Delta_y$) is randomly selected between -64 pixels and 64 pixels.
The width/height of the fake target is randomly selected between 32 pixels and 128 pixels.
The perturbed search image is generated as follows:
\begin{equation}
\tilde{\textbf x} = A(\textbf x, p_k, (l^x, l^y), (w, h)),
\end{equation}
where $(l^x, l^y)$ and $(w, h)$ represents the position and size of the fake target relative to the search image, respectively. $A$ is patch application operator \cite{patch} which first resizes the patch $p_k \in \mathbb{R}^{128\times 128\times 3}$ to $\hat{p}_k \in \mathbb{R}^{w\times h\times 3}$, and then applies the resized patch $\hat{p}_k$ to the search image $\textbf x$ at location $(l^x,l^y)$.
